Learning and memory with complex synapses

### 2012-11-14 Cosyne/Abstract.tex
cosyne abstract: refs

We consider the storage of long term memories through synaptic modifications in existing networks.
Recent experimental work suggests that single synapses are digital, in the sense that, from the perspective of extracellular physiology, they can only take on a finite number of discrete values for their strength.
This imposes catastrophic limits on the memory capacity of classical models of memory that have relied on a continuum of analog synaptic strengths [Amit and Fusi, Network: Computation in Neural Systems (1992)]\nocite{amit1992constraints}.

@@

We can use the transition probabilities to optimize features of the SNR, thereby proving upper limits on the performance of the synapse.
For example we show that the area under the curve has an upper bound that grow linearly with the number of internal states.
This upper limit is saturated by a particular transition network with a linear chain topology,
We also find an upper limit on the instantaneous value of the SNR at any time.
This allows us to bound the length of time that any memory can be recovered, and hence the memory capacity of such synapses.

>>>>

We consider the storage of long term memories through synaptic modifications in existing networks.
Recent experimental work suggests that single synapses are digital, in the sense that, from the perspective of extracellular physiology, they can only take on a finite number of discrete values for their strength [Bliss and Collingridge, Nature (1993), Bredt and Nicoll, Neuron (2003)]\nocite{Bliss1993,*Bredt2003361}.
This imposes catastrophic limits on the memory capacity of classical models of memory that have relied on a continuum of analog synaptic strengths [Amit and Fusi, Network: Computation in Neural Systems (1992)]\nocite{amit1992constraints}.

@@

We can use the transition probabilities to optimize features of the SNR, thereby proving upper limits on the performance of the synapse.
For example we show that the area under the curve has an upper bound that grows linearly with the number of internal states.
This upper limit is saturated by a particular transition network with a linear chain topology,
We also find an upper limit on the instantaneous value of the SNR at any time.
This allows us to bound the length of time that any memory can be recovered, and hence the memory capacity of such synapses.
